Adaptative neighbouring methods applied to telephonic base stations

### 2024-08-23 article.tex
conclusion

\begin{IEEEkeywords}
    Neighbours, Telecommunication, Base station, $k$-NN, Adaptative.
\end{IEEEkeywords}

\section{Introduction}
    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.

@@

    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called Base Station (BS). These BSs give the cell network coverage so that voice, data, and other kinds of content may be transmitted.

@@

    Another method consists in the using the Delaunay triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
    [insert Delaunay neighbouring reference]

@@

\section{Related works\label{sec:rel_works}}
    \noindent When looking for neighbours, the first method that comes in mind is $k$-NN.

@@

\section{Contributions\label{sec:contrib}}
    \noindent In Section~\ref{sec:overview}, we have seen that we can find the neighbours of BSs by combining a potential neighbouring graph and filtration criteria. This methodology gives pretty good results \cite{art_del_paq}.

@@

        \subsubsection{Distance and angle criterion}
            As seen in Section~\ref{sec:overview}, after having found potential neighbours for each BS, this connexions needs to be filtrated. However, this applies the same distance and angle threshold for all BSs, without taking in account the difference of density.

@@

        In the future, there will be method to compare our results with a reference. [pas sûr si on garde ca]
        \begin{figure}
            \centering
            \includegraphics[width=3.5in]{images/illus_graphs/final_neighs_del_da.png}
            \caption{The final neighbouring graph.}
            \label{fig:final_neighs}
        \end{figure}

\section{Conclusion\label{sec:ccl}}
    [Ouverture: prendre en compte les zazimuths]

>>>>

\begin{IEEEkeywords}
    Neighbours, Telecommunication, Base station, $k$-NN, Adaptative.
\end{IEEEkeywords}
\section{Introduction}
    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.

@@

    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called base station (BS). These BSs give the cell network coverage so that voice, data, and other kinds of content may be transmitted.

@@

    Another method consists in the using the Delauney triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
    [insert Delauney neighbouring reference]

@@

\section{Related works\label{sec:rel_works}}
    \noindent

@@

\section{Contributions\label{sec:contrib}}
    \noindent In section~\ref{sec:overview}, we have seen that we can find the neighbours of BSs by combining a potential neighbouring graph and filtration criteria. This methodology gives pretty good results \cite{art_del_paq}.

@@

        \subsubsection{Distance and angle criterion}
            As seen in section~\ref{sec:overview}, after having found potential neighbours for each BS, this connexions needs to be filtrated. However, this applies the same distance and angle threshold for all BSs, without taking in account the difference of density.

@@

        \begin{figure}
            \centering
            \includegraphics[width=3.5in]{images/illus_graphs/final_neighs_del_da.png}
            \caption{The final neighbouring graph.}
            \label{fig:final_neighs}
        \end{figure}

\section{Conclusion\label{sec:ccl}}
    The presented method successfully detects the neighbourhood of the base stations from Orange using 4G technology in France. It is an upgrade from previously introduced methods because it locally takes into account the density of base station to compute the neighbouring relationships.

    Future works could evaluate its performance on other providers or even, using another database, in another country.

    Another important work would be to create an exact method to detect the neighbours of each base station, however the computationnal cost. It would allow to have an objective element of reference when tuning the parameters of the method presented here, that is the categories of $\gamma_p$ values and their associated threshold in the criterias. For that, it would be interesting to use a database including the azimuth angle of each base station (the direction of each antenna of the base station) to simulate the coverage of each base station and therefore be able to predict when they overlap, which means the two base stations are neighbours.

    Finally, this work can be used inside bigger work that are being made in order to predict the users behaviour inside the telephonic network.
